### 2017-04-28 src/hardness.tex
done for today
foo

In this section we show that the problem in its general form cannot be
approximated at all assuming $P \neq NP$.
\todo{Is it true ?}
We also show that the problem remains NP-hard even when restricted to DAGS.

@@

We now show that the problem restricted to DAG is still NP-hard.
We present a polynomial reduction from partition.
Let $\{a_1, \ldots, a_n\}$ be an instance of the partition problem, 
consider the instance of the VPN problem 
$D_v = (V_v, A_v), D_p = ({v}, \emptyset)$, 
where:
\begin{align}
V_v = \{s, t\} \cup \{v_1^+, \ldots, v_n^+\} \cup \{v_1^-, \ldots, v_n^-\}
\\
A_v = \{\{v_i^+, v_i^-\} \times \{v_{i + 1}^+, v_{i + 1}^-\}\} 
\cup \{(s, v_1^+), (s, v_1^-), (v_n^+, t), (v_n^-, t)\}
&&
\forall i \in [n-1]
\\
p_d(v_i^+) = a_i && \forall i \in [n]
\\
p_d(v_i^-) = 0 && \forall i \in [n]
\\
c(v_i^+, v) = 0 && \forall i \in [n]
\\
c(v_i^-, v) = a_i && \forall i \in [n] 
\\
p_c(v) = \inv{2}\sum_{i = 1}^n a_i
\end{align}
Note that the bandwidth function does not plays a role here because the physical graph
is just a single vertex.

@@

>>>>

The VPN problem, in its general form, can not be approximated at all.
To see this, consider an instance of the problem where the virtual graph is a simple path of $n = |V_p|$ vertices, $p_d \equiv p_c \equiv 1$, 
$b_d \equiv b_c \equiv 1$,
and $c \equiv 0$.
In this instance any feasible embedding has cost 0, furthermore, one exists if and only if there is an Hamiltonian path in the physical graph.
Thus, any algorithm that returns a feasible embedding also finds an Hamiltonian path.

We also show that the problem remains NP-hard even when restricted to DAGS.

@@

We now show that the problem restricted to DAG is still NP-hard.
We present a polynomial reduction from partition.
Let $\{a_1, \ldots, a_n\}$ be an instance of the partition problem, 
consider the instance of the VPN problem 
$D_v = (V_v, A_v), D_p = ({v}, \emptyset)$, 
where:
\begin{align}
V_v = \{s, t\} \cup \{v_1^+, \ldots, v_n^+\} \cup \{v_1^-, \ldots, v_n^-\}
\\
A_v = \{\{v_i^+, v_i^-\} \times \{v_{i + 1}^+, v_{i + 1}^-\}\} 
\cup \{(s, v_1^+), (s, v_1^-), (v_n^+, t), (v_n^-, t)\}
&&
\forall i \in [n-1]
\\
p_d(v_i^+) = a_i && \forall i \in [n]
\\
p_d(v_i^-) = 0 && \forall i \in [n]
\\
c(v_i^+, v) = 0 && \forall i \in [n]
\\
c(v_i^-, v) = a_i && \forall i \in [n] 
\\
p_c(v) = \frac{1}{2}\sum_{i = 1}^n a_i
\end{align}
Note that the bandwidth function does not plays a role here because the physical graph
is just a single vertex.

@@

\todo{finish}

### 2017-04-28 src/problem.tex
foo

We are given a virtual DAG $D_v = (V_v, A_v)$ 
with source and destination vertices $s_v, t_v$ respectively, 
a physical DAG $D_p = (V_p, A_p)$
with source and destination vertices $s_p, t_p$ respectively,
demand functions $p_d : V_v \to \R$, $b_d : E_v \to \R$,
capacity functions $p_c : V_p \to \R$, $b_c : E_p \to \R$,
and a cost function $c: V_v \times V_p \to \R$.

Given a virtual $s_vt_v$-path $p$ of length $l$,
let $i_1, \ldots, i_l$ be the indices of the vertices of this path.
We denote a partition of $p$ into subpaths by the indices of the last vertex in
each subpath i.e. we use $j_1, \ldots, j_k$ to denote the partition 
$((v_{i_1}, \ldots, v_{i_{j_1}}), \ldots, (v_{i_{j_{k-1} + 1}}, \ldots,
v_{i_{j_k}}))$.
Given a partition $(j_1, \ldots, j_k)$ we denote by $V(j_i)$ the vertices of the
$i$th subpath.
A (feasible) \emph{embedding} of a virtual path into the physical graph 
w.r.t partition $P = (j_1, \ldots,j_k)$ is a mapping $\psi : P \to V_p$ such that
for all $1 \leq i \leq k$ it holds that:
\begin{enumerate}
  \item $p_c(\psi(j_i)) \geq \sum_{v \in V(j_i)} p_d(v)$
  \item There is a physical path, $\pi_i$ from $\psi(j_i)$ to $\psi(j_{i+1})$ with a
  bottleneck at least $b_d(v_{j_i}, v_{j_{i+1}})$.
\end{enumerate}
The \emph{cost} of a (feasible) embedding, $e_P$ is given by:
$\sum_{i = 1}^k \sum_{v \in V(j_i)} c(v, e_P(j_i))$.

>>>>

We are given a virtual directed graph $D_v = (V_v, A_v)$ 
with source and destination vertices $s_v, t_v$ respectively, 
a physical directed graph $D_p = (V_p, A_p)$
with source and destination vertices $s_p, t_p$ respectively,
demand functions $p_d : V_v \to \R$, $b_d : E_v \to \R$,
capacity functions $p_c : V_p \to \R$, $b_c : E_p \to \R$,
and a cost function $c: V_v \times V_p \to \R$.

Given a virtual $s_vt_v$-path $p$ of length $l$,
let $i_1, \ldots, i_l$ be the indices of the vertices of this path.
We denote a partition of $p$ into subpaths by the indices of the last vertex in
each subpath i.e. we use $j_1, \ldots, j_k$ to denote the partition 
$((v_{i_1}, \ldots, v_{i_{j_1}}), \ldots, (v_{i_{j_{k-1} + 1}}, \ldots,
v_{i_{j_k}}))$.
Given a partition $(j_1, \ldots, j_k)$ we denote by $V(j_i)$ the vertices of the
$i$th subpath.
A (feasible) \emph{embedding} of a virtual path into the physical graph 
w.r.t partition $P = (j_1, \ldots,j_k)$ is a mapping $\psi : P \to V_p$ such that
for all $1 \leq i \leq k$ it holds that:
\begin{enumerate}
  \item $p_c(\psi(j_i)) \geq \sum_{v \in V(j_i)} p_d(v)$
  \item There is a physical path, $\pi_i$ from $\psi(j_i)$ to $\psi(j_{i+1})$ with a
  bottleneck at least $b_d(v_{j_i}, v_{j_{i+1}})$.
  \item $\bigcup_{i = 1}^k \pi_i$ is a simple path.
\end{enumerate}
The \emph{cost} of a (feasible) embedding, $e_P$ is given by:
$\sum_{i = 1}^k \sum_{v \in V(j_i)} c(v, e_P(j_i))$.
